---
title: "Fitting Growth Curves to Estimated Tuber Weight (2024)"
author: "Yuto Imachi"
output: html_document
---

```{r}
script_name <- "032_2024_TW_Forecasting"
```

# Project Setup
```{r}
project_dir <- normalizePath("..")
data_dir <- file.path(project_dir, "01_data")
output_dir <- file.path(project_dir, "outputs")
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

# Script-specific directories
midstream_dir <- file.path(output_dir, script_name, "midstream")
results_dir   <- file.path(output_dir, script_name, "results")

# Create directories recursively (parents=True 相当)
dir.create(midstream_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_dir, recursive = TRUE, showWarnings = FALSE)
```

# Import Libraries
```{r}
library(tidyverse)
library(nlme)

library(ggplot2)
```


# Data Loading and Preprocessing
## _Obsearved Data 
```{r}
rawdata_path = file.path(data_dir,
                         "FT_2024_df.csv") # 2023用
df_raw = read.csv(rawdata_path, header = T)
df_raw = df_raw[,seq(2,length(colnames(df_raw)))]
df_raw[1:10,]
```

```{r}
df <- df_raw
cols_Label <- c(
  "Temperature",
  "Density",
  "block",
  "subblock",
  "ridge",
  "plot",
  "plot_ridge_ind",
  "HarvTime"
)

df[cols_Label] <- lapply(df[cols_Label], as.factor)
df["block"] <- lapply(df["block"], as.character)
df[df$block == "TRUE","block"] <- "T"

df$Temperature <- factor(df$Temperature, levels = c("Low", "Mid-Short", "Mid-Long", "High")) 
df$Density <- factor(df$Density, levels = c("sparse", "standard", "dense")) 
df$block<- factor(df$block)

df[is.na(df)] <- 0
df <- arrange(df, df$block, df$DAS, df$plot, df$ridge)
df[1:10,]
```

```{r}
df2 <- df
df2[cols_Label] <- lapply(df2[cols_Label], as.factor)
df2$DAS <- as.integer(as.character(df2$DAS))
df2[1:10,]
```

## _Load Estimation Results
```{r}
year_now <- "2024"

model_timestamp_config_df <- read.csv(
  file.path(data_dir, "0_model_timestamp_config.csv"),
  row.names = 1,header = TRUE,
  stringsAsFactors = FALSE,
  colClasses = "character",
  check.names = FALSE
)
model_timestamp_config_df[] <- lapply(
  model_timestamp_config_df,
  function(x) gsub('"', "", x)
)

modeltime_now <- model_timestamp_config_df["RandomCV", year_now]
```

```{r}
modeltime_now_dir <-file.path(output_dir, 
                              "022_2024_TW_Estimation", 
                              "results", 
                              paste0("merge_pred_df_melt_",modeltime_now)
)
modeltime_now_dir
```

```{r}
results_modeltime_now_dir <- paste0(results_dir,"/",
                                    "modeltime_now", "_", modeltime_now, "/")
dir.create(results_modeltime_now_dir)
```

```{r}
eval_df_all <- data.frame(stra_name = character(0),
                          fitting_name = character(0),
                          r = character(0),
                          r2 = character(0),
                          RMSE = character(0))
```

```{r}
stra_names_li <- read.csv(file.path(modeltime_now_dir, "stra_names_df.csv"))["stra_names"][,1]
stra_names_li <-stra_names_li[
  grepl("ImgType-Full", stra_names_li) &
    grepl("SampRate-100", stra_names_li) &
    grepl("SampMetho-random", stra_names_li)
]

for (stra_i in 1:length(stra_names_li)){
  if (stra_i !=1){
    next
  }
  stra_name_now <- stra_names_li[stra_i]
}
```

```{r}
stra_names_li
```

```{r}
get_ml_pred_df <- function(modeltime_now_dir,stra_name_now){
  ml_pred_df <- read.csv(paste0(modeltime_now_dir,"/",
                                stra_name_now,".csv"), 
                         header = T, row.names = 1)

  
  ml_pred_df[cols_Label] <- lapply(ml_pred_df[cols_Label], as.factor)

  ml_pred_df$Temperature <- factor(ml_pred_df$Temperature, levels = c("Low", "Mid-Short", "Mid-Long", "High")) 
  ml_pred_df$Density <- factor(ml_pred_df$Density, levels = c("sparse", "standard", "dense")) 
  
  y <- "Wei_all_per_m2"
  
  ml_pred_df <- ml_pred_df %>%
  select(-DAS)
  
  ml_pred_df <- ml_pred_df %>%
    rename(c("DAS" = pred_DAS)) %>%
    rename(!!y := value) %>%
    select(-c( index)) 
  
  pl_ri_in_li <- sort(unique(ml_pred_df$plot_ridge_ind))
  pl_ri_in_ord <- factor(pl_ri_in_li, levels = pl_ri_in_li)
  
  return(ml_pred_df)
}
```

```{r}
ml_pred_df <- get_ml_pred_df(modeltime_now_dir,stra_name_now)
ml_pred_df[1:10,]
```

## _Define Evaluation Metric Functions
```{r}
RMSE <- function(ob, pre){
  temp <- sqrt(mean((ob-pre)^2))
  return(temp)
}
```

```{r}
R2 <- function(ob, pre) {
  ss_total <- sum((ob - mean(ob))^2)    
  ss_residual <- sum((ob - pre)^2)     
  r2 <- 1 - (ss_residual / ss_total)   
  return(r2)
}
```

## _Creating Grouped Data
```{r}
make_grouped_byplot <- function(Test_alp, df, CV = FALSE, inp_HT = "5", future_day, debag = FALSE){
  fct2_df <- df
  ml_pred_df <- df
  if (CV == T){
    Train_alp <- LETTERS[1:4][!(LETTERS[1:4] %in% Test_alp)]
  
    fct2_df <- ml_pred_df[!((ml_pred_df$HarvTime == "6") & (ml_pred_df$Group %in% Test_alp) & (ml_pred_df$DAS == future_day)),] 
  }
  
  if (inp_HT == "5"){
    fct2_df <- fct2_df[!((fct2_df$DAS == future_day)), ]
  }

  fct2_df <- fct2_df[(fct2_df$HarvTime == "5")|(fct2_df$HarvTime == "6"),]

  y <- "Wei_all_per_m2" 
  if (debag == TRUE) print(y)

  
  df_now <- fct2_df[,c(y,"Temperature", "Density", "subblock","HarvTime", "DAS", "plot_ridge_ind")] 
  df_now$Temperature <- factor(df_now$Temperature,levels = c("Low", "Mid-Short", "Mid-Long", "High"))
  df_now$Density <- factor(df_now$Density,levels = c("sparse", "standard", "dense"))
  df_now$block <- ordered(as.factor(df_now$subblock))
  
  df_now$DAS <- df_now$DAS
  df_now$ind <- df_now$plot_ridge_ind
  df_now$ind <- ordered(as.factor(df_now$ind))
  df_now <- df_now[!is.na(df_now[,y]),]
  
  fml_now <- paste(y, "~", "block + Temperature + Density + HarvTime + DAS + ind ", sep = "") 
  df_agg_now <- aggregate(as.formula(fml_now) , data = df_now, FUN = mean)
  df_agg_now$Temperature <- factor(df_agg_now$Temperature,levels = c("Low", "Mid-Short", "Mid-Long", "High"))
  df_agg_now$Density <- factor(df_agg_now$Density,levels = c("sparse", "standard", "dense"))
  
  
  df_now <- arrange(df_now, plot_ridge_ind, DAS)
  if (debag == TRUE) print(df_now[1:10,])
  
  ## Reshape Data for nlme Mixed-Effects Model
  FML_1 <- paste(y, "~", "DAS|ind", sep = "") 
  DF_now <- groupedData(as.formula(FML_1), 
                        data = df_agg_now,
                        outer = ~ Temperature*Density
                        )
  
  plot(DF_now, outer = ~ Temperature*Density, inner = ~block, layout = c(4,3), aspect = 0.75,key = NULL)
  
  return(DF_now)
}
```


```{r}
Test_alp <- c("B")
CV_TorF <- F
future_day <- 109
DF_now <- make_grouped_byplot(Test_alp = Test_alp,
                              df = ml_pred_df, 
                              CV = CV_TorF, 
                              future_day = future_day, 
                              debag = TRUE)
```

```{r}
make_plot_obs <- function(DF_now, df2, stra_name_now) {
  g <- ggplot(NULL)
  g <- g + geom_line(data = DF_now, aes(x = DAS, y = Wei_all_per_m2, group = ind)) 
  g <- g + geom_point(data = DF_now, aes(x = DAS, y = Wei_all_per_m2, group = ind))
  g <- g + theme_bw()
  g <- g + geom_point(data = df2[df2$HarvTime == "6", ], aes(x = DAS, y = Wei_all_per_m2), shape = 21)
  ggsave(paste0(results_modeltime_now_dir, "obs", "_", stra_name_now, ".png"), g)
}

```

```{r}
make_plot_obs(DF_now, df2, stra_name_now)
```

# Fitting the growth curve
## _Separate (nlsList) Growth Curve Fitting
```{r}
fitting_name_now <- "nlsList"
```

```{r}
y <- "Wei_all_per_m2"
model_now <-  paste0(y, " ~ SSgompertz(DAS, Asym,b2,b3)")
model_formula <- as.formula(model_now)

fit_nlsList <- function(df,y,model_formula){
  DF_now <- df

  fmlnow_lis <- nlsList(model_formula, 
                      data = DF_now)
  fmlnow_lis 
  plot(intervals(fmlnow_lis), layout = c(3,1))
  return(fmlnow_lis)
}
```


```{r}
fmlnow_lis <- fit_nlsList(DF_now,y, model_formula)  
fmlnow_lis
```

```{r}
cal_future_y_nlsList <- function(DF_now, fmlnow_lis, future_day){
  pred_df <- data.frame(plot_ridge_ind = rownames(coef(fmlnow_lis)), Prediction = NA)
  for(i in 1:length(unique(DF_now$ind))) {
    coef_i <- coef(fmlnow_lis)[i, ]
    pred_df$Prediction[i] <- SSgompertz(future_day, coef_i[1, "Asym"], coef_i[1, "b2"], coef_i[1, "b3"])
  }
  return(pred_df)
}
```

```{r}
pred_df_nlsList <- cal_future_y_nlsList(DF_now, fmlnow_lis, future_day)
pred_df_nlsList[1:10,]
```

### __Visualization of Separate Model Results
```{r}
make_plot_nlsList <- function(df2, DF_now, fmlnow_lis, stra_name_now, future_day){
  
  png(paste0(results_modeltime_now_dir, "nlsList", "_", stra_name_now, ".png"), width = 450, height = 400)
  plot(DF_now$DAS, DF_now$Wei_all_per_m2,
       main = "Gompertz Curve for Each plot", xlab = "", ylab = "",
       xlim= range(0,120), ylim = range(0, 7000),
       pch = 0)
  par(new = T)
  
  plot(rep(future_day,length(df2[df2$HarvTime==6, y])), df2[df2$HarvTime==6, y], 

       xlab = "", ylab = "", xlim= range(0,120), ylim = range(0, 7000),
       pch = 4)
  par(new = T)

  DAS_seq <- seq(0, max(DF_now$DAS), length.out = 100)
  DAS_seq_fu <- seq(max(DF_now$DAS), 120, length.out = 100)
  
  
  for(i in 1:length(unique(DF_now$ind))) {
    coef_i <- coef(fmlnow_lis)[i, ]
    pred <- SSgompertz(DAS_seq, coef_i[1, "Asym"], coef_i[1, "b2"], coef_i[1, "b3"])
    lines(DAS_seq, pred, lwd = 0.5, lty = 1) 
    pred_fu <- SSgompertz(DAS_seq_fu, coef_i[1, "Asym"], coef_i[1, "b2"], coef_i[1, "b3"])
    lines(DAS_seq_fu, pred_fu, col = "grey", lwd = 0.5, lty = 2) 
  
    
  }
  dev.off()
}
```

```{r}
make_plot_nlsList(df2, DF_now, fmlnow_lis, stra_name_now, future_day)
```

```{r}
make_compe_df <- function(pred_df, df2){
  compe_df <- left_join(pred_df, df2[c(cols_Label, y)], by = "plot_ridge_ind") 
}
```

```{r}
compe_df_nlsList <- make_compe_df(pred_df_nlsList, df2)
```


```{r}
get_eval_values <- function(compe_df, stra_name_now, fitting_name, isnull = FALSE){
  if (isnull==FALSE){
    
    cor_now <- (cor(compe_df$Wei_all_per_m2, compe_df$Prediction))
    r2_now <- (R2(compe_df$Wei_all_per_m2, compe_df$Prediction)) 
    RMSE_now <- (RMSE(compe_df$Wei_all_per_m2, compe_df$Prediction))　
    
    eval_df <- data.frame(stra_name = stra_name_now,
                          fitting_name = fitting_name,
                          r = cor_now,
                          r2 = r2_now,
                          RMSE = RMSE_now)    
  }
  
  if (isnull==TRUE){
    cor_now <- NA
    r2_now <- NA
    RMSE_now <- NA
    eval_df <- data.frame(stra_name = stra_name_now,
                          fitting_name = fitting_name,
                          r = cor_now,
                          r2 = r2_now,
                          RMSE = RMSE_now)        
  }
  
  return(eval_df)
}
```

```{r}
eval_df_nlsList <- get_eval_values(compe_df_nlsList, stra_name_now, fitting_name_now, isnull = FALSE)
eval_df_nlsList
```


```{r}
eval_df_all <- rbind(eval_df_all, eval_df_nlsList)
eval_df_all
```

```{r}
make_scatter <- function(compe_df, eval_df_now, fitting_name_now){
  
  x_vals <- 1:10000
  
  cor_now <- eval_df_now$r
  r2_now <- eval_df_now$r2
  RMSE_now <- eval_df_now$RMSE
  
  g <- ggplot(compe_df, aes(x=Wei_all_per_m2, y=Prediction))
  g <- g + geom_point() 
  g <- g + geom_abline(slope = 1, intercept = 0) 
  g <- g + xlab("observed") + ylab("predicted")
  g <- g + xlim(c(2500,8000)) + ylim(c(2500, 8000)) + theme(aspect.ratio = 1)
  g <- g + annotate("text", x = 6000, y = 4500, hjust=0, size = 5,
                    label = paste0("r: ", as.character(round(cor_now, digits = 2)), "\n",
                                   "R2: ", as.character(round(r2_now, digits = 2)), "\n",
                                   "RMSE: ", as.character(round(RMSE_now, digits = 2))))
  
  ggsave(paste0(results_modeltime_now_dir, "scatter_",fitting_name_now, "_", stra_name_now, ".png"))

}
```

```{r}
make_scatter(compe_df_nlsList, eval_df_nlsList, fitting_name_now)
```

## _Mixed-Effects (nlme) Growth Curve Fitting
```{r}
fitting_name_now <- "nlme"
```

```{r}
fit_nlme <- function(df, model_now, fmlnow_lis){
  
  DF_now <- df
  fm1now_nlme <- tryCatch({
    nlme(as.formula(model_now), 
         data = DF_now,
         fixed = Asym + b2 + b3 ~ 1,
         random  = pdDiag(Asym + b2 + b3 ~ 1), 
         na.action = NULL, 
         naPattern = ~ !is.na(Wei_all_per_m2) ,
         start = fixef(fmlnow_lis),
         control = nlmeControl(maxIter = 100, niterEM = 100, tolerance = 1e-5))
  }, error = function(e){
    cat("error in nlme:\n", e$message, "\n")
    NULL
  })
}
```


```{r}
fm1now_nlme <- fit_nlme(DF_now, model_now, fmlnow_lis) 
fm1now_nlme
```


```{r}
cal_future_y_nlme <- function(DF_now, fm1now_nlme, future_day){
  
  fixed_effects <- fixef(fm1now_nlme)
  random_effects <- ranef(fm1now_nlme)

  pred_df <- data.frame(plot_ridge_ind = rownames(random_effects), Prediction = NA) 
  DAS_seq <- seq(0, max(DF_now$DAS), length.out = 100)
  DAS_seq_fu <- seq(max(DF_now$DAS), 120, length.out = 100)
  
  for(i in 1:nrow(random_effects)) {
    Asym_i <- fixed_effects["Asym"] + random_effects[i, "Asym"]
    b2_i <- fixed_effects["b2"] + random_effects[i, "b2"]
    b3_i <- fixed_effects["b3"] + random_effects[i, "b3"]
    pred_i <- SSgompertz(DAS_seq, Asym_i, b2_i, b3_i )
    pred_i_fu <- SSgompertz(DAS_seq_fu, Asym_i, b2_i, b3_i )
    pred_df$Prediction[i] <- SSgompertz(future_day, Asym_i, b2_i, b3_i)
  }
  
  return(pred_df)
}
```

```{r}
pred_df_nlme <- cal_future_y_nlme(DF_now, fm1now_nlme, future_day)
pred_df_nlme[1:10,]
```


### __Visualization of Mixed-Effects Model Results
```{r}
make_plot_nlme <- function(df2, DF_now, fm1now_nlme, stra_name_now, future_day){
  
  png(paste0(results_modeltime_now_dir, "nlme", "_", stra_name_now, ".png"), width = 450, height = 400)
  plot(DF_now$DAS, DF_now$Wei_all_per_m2,
       main = "Gompertz Curve for Each plot", xlab = "", ylab = "",
       xlim= range(0,120), ylim = range(0, 7000),
       pch = 0)
  par(new = T)
  
  plot(rep(future_day,length(df2[df2$HarvTime==6, y])), df2[df2$HarvTime==6, y], 
       
       xlab = "", ylab = "", xlim= range(0,120), ylim = range(0, 7000),
       pch = 4)
  par(new = T)

  DAS_seq <- seq(0, max(DF_now$DAS), length.out = 100)
  DAS_seq_fu <- seq(max(DF_now$DAS), 120, length.out = 100)
  
  fixed_effects <- fixef(fm1now_nlme)
  random_effects <- ranef(fm1now_nlme)
  
  for(i in 1:nrow(random_effects)) {
    Asym_i <- fixed_effects["Asym"] + random_effects[i, "Asym"]
    b2_i <- fixed_effects["b2"] + random_effects[i, "b2"]
    b3_i <- fixed_effects["b3"] + random_effects[i, "b3"]
    pred_i <- SSgompertz(DAS_seq, Asym_i, b2_i, b3_i )
    pred_i_fu <- SSgompertz(DAS_seq_fu, Asym_i, b2_i, b3_i )
    lines(DAS_seq, pred_i, col = "black", lwd = 0.25, lty = 1)
    lines(DAS_seq_fu, pred_i_fu, col = "grey", lwd = 0.25, lty = 2)

  }
  dev.off()
}
```

```{r}
make_plot_nlme(df2, DF_now, fm1now_nlme, stra_name_now, future_day)
```

```{r}
compe_df_nlme <- make_compe_df(pred_df_nlme, df2)
compe_df_nlme[1:10,]
```


```{r}
eval_df_nlme <- get_eval_values(compe_df_nlme, stra_name_now, fitting_name_now)
eval_df_nlme
```

```{r}
eval_df_all <- rbind(eval_df_all, eval_df_nlme)
eval_df_all
```

```{r}
make_scatter(compe_df_nlme, eval_df_nlme, fitting_name_now)
```

## _Run nls and nlme Models in a Loop
```{r}
nlslist_obj_dirname <- file.path(midstream_dir,"nlslist_obj")
nlme_obj_dirname <- file.path(midstream_dir, "nlme_obj")

dir.create(nlslist_obj_dirname)
dir.create(nlme_obj_dirname)
```

```{r}
for (blo_now in c("bloAll")){ 
  eval_df_all <- data.frame(stra_name = character(0),
                            fitting_name = character(0),
                            r = character(0),
                            r2 = character(0),
                            RMSE = character(0))
  
  
  for (stra_i in 1:length(stra_names_li)){

    stra_name_now <- stra_names_li[stra_i]
    print(stra_name_now)
    ml_pred_df <- get_ml_pred_df(modeltime_now_dir,stra_name_now)
    df2 <- df
    df2[cols_Label] <- lapply(df2[cols_Label], as.factor)
    
    if (blo_now != "bloAll"){
      ml_pred_df <- ml_pred_df[ml_pred_df$subblock == str_sub(blo_now, -1),]
      df2 <- df2[df2$subblock == str_sub(blo_now, -1),]
    }
    
    Test_alp <- c("B")
    CV_TorF <- F
    future_day <- 109
    
    DF_now <- make_grouped_byplot(Test_alp = Test_alp, df = ml_pred_df, CV = CV_TorF, future_day = future_day)
    
    make_plot_obs(DF_now, df2, stra_name_now)
    
    # nlsList
    fitting_name_now <- "nlsList"
    fmlnow_lis <- fit_nlsList(DF_now,y, model_formula)
    saveRDS(fmlnow_lis, 
            file.path(nlslist_obj_dirname, 
                      paste0(fitting_name_now, "_" , stra_name_now, ".rds")
            ) 
    )
    fmlnow_lis <- readRDS(file.path(nlslist_obj_dirname,
                                    paste0(fitting_name_now, "_" , stra_name_now, ".rds")
    )
    )
    pred_df_nlsList <- cal_future_y_nlsList(DF_now, fmlnow_lis, future_day)
    make_plot_nlsList(df2, DF_now, fmlnow_lis, stra_name_now, future_day)
    compe_df_nlsList <- make_compe_df(pred_df_nlsList, df2)
    eval_df_nlsList <- get_eval_values(compe_df_nlsList, stra_name_now, fitting_name_now)
    eval_df_all <- rbind(eval_df_all, eval_df_nlsList)
    make_scatter(compe_df_nlsList, eval_df_nlsList, fitting_name_now)
    
    # nlme
    fitting_name_now <- "nlme"
    fm1now_nlme <- fit_nlme(DF_now, model_now, fmlnow_lis)
    saveRDS(fm1now_nlme,
            file.path(nlme_obj_dirname, 
                      paste0(fitting_name_now, "_" , stra_name_now, ".rds")
                      )
            ) 
    fm1now_nlme <- readRDS(file.path(nlme_obj_dirname, 
                                     paste0(fitting_name_now, "_" , stra_name_now, ".rds")
                                     )
                           )
    if (is.null(fm1now_nlme)==FALSE){
      pred_df_nlme <- cal_future_y_nlme(DF_now, fm1now_nlme, future_day)
      make_plot_nlme(df2, DF_now, fm1now_nlme, stra_name_now, future_day)
      compe_df_nlme <- make_compe_df(pred_df_nlme, df2)
      eval_df_nlme <- get_eval_values(compe_df_nlme, stra_name_now, fitting_name_now)
      eval_df_all <- rbind(eval_df_all, eval_df_nlme)
      make_scatter(compe_df_nlme, eval_df_nlme, fitting_name_now)
    }
    
    else{
      eval_df_nlme <- get_eval_values(compe_df_nlme, stra_name_now, fitting_name_now, isnull = TRUE)
      eval_df_all <- rbind(eval_df_all, eval_df_nlme)
    }
  }
  write.csv(x = eval_df_all,
            file = file.path(results_modeltime_now_dir,
                             paste0("eval_df_all", "_", blo_now, ".csv")
            )
  )
}
```


# Making Figure in Paper
```{r}
anno_fig_li <- c("bloCV-Non_ImgType-Full_SampRate-100_SampMetho-random_Rep-1.csv") 
```

## _Plotting the separate model curve
```{r}
make_plot_nlsList4 <- function(df2, DF_now, fmlnow_lis, stra_name_now, future_day) {
  
  png(file.path(results_dir, 
                paste0("pap_nlsList_", stra_name_now, ".png")
                ),
      width = 1800, height = 1600)

  par(tcl = 1, 
      mgp = c(3, 3, 0), 
      mar = c(20, 20, 20, 5))  
  plot(jitter(DF_now$DAS, amount = 1), DF_now$Wei_all_per_m2,
       main = "Separate model in 2024",
       xlab = "", 
       ylab = "",
       xlim = c(0, 120), 
       ylim = c(0, 7000),
       pch = 0,
       cex = 3,
       cex.axis = 4,
       cex.lab = 4,
       cex.main = 8,
       las = 1)
  
  par(new = TRUE)

  plot(jitter(rep(future_day, length(df2[df2$HarvTime == 6, y])), amount = 1),
       df2[df2$HarvTime == 6, y],
       xlab = "", ylab = "", 
       xlim = c(0, 120), ylim = c(0, 7000),
       pch = 4,
       cex = 3,
       cex.axis = 4,
       cex.lab = 4,
       cex.main = 8,
       las = 1)
  
  par(new = TRUE)

  DAS_seq <- seq(0, max(DF_now$DAS), length.out = 100)
  DAS_seq_fu <- seq(max(DF_now$DAS), 120, length.out = 100)

  for(i in 1:length(unique(DF_now$ind))) {
    coef_i <- coef(fmlnow_lis)[i, , drop = FALSE] 
    pred    <- SSgompertz(DAS_seq,    coef_i[1, "Asym"], coef_i[1, "b2"], coef_i[1, "b3"])
    pred_fu <- SSgompertz(DAS_seq_fu, coef_i[1, "Asym"], coef_i[1, "b2"], coef_i[1, "b3"])
    
    lines(DAS_seq,    pred,    lwd = 1, lty = 1)
    lines(DAS_seq_fu, pred_fu, col = "grey", lwd = 1, lty = 2)
  }

  title(xlab = expression("DAS (days)"), line = 8, cex.lab = 5)
  title(ylab = expression(paste("Tuber Fresh Weight ( "*g~m^{-2}*" )")), line = 12, cex.lab = 5)

  legend("topleft", 
         legend = c("estimated value", "observed value", "fitted curve", "projected curve"), 
         pch = c(0, 4, NA, NA), 
         lty = c(NA, NA, 1, 2), 
         col = c("black", "black", "black", "grey"), 
         pt.cex = 3, 
         cex = 5,
         bty = "n", 
         lwd = c(3, 3, 3, 3))

  dev.off()
}

```

## _Plotting the mixed model curve
```{r}
make_plot_nlme4 <- function(df2, DF_now, fm1now_nlme, stra_name_now, future_day) {
  
  png(file.path(results_dir, 
                paste0("pap_nlme_", stra_name_now, ".png")
                ),
      width = 1800, height = 1600
      )

  par(tcl = 1, 
      mgp = c(3, 3, 0), 
      mar = c(20, 20, 20, 5))  
  
  plot(jitter(DF_now$DAS, amount = 1), DF_now$Wei_all_per_m2,
       main = "Mixed-Effects Model in 2024",
       xlab = "", 
       ylab = "",
       xlim = c(0, 120),
       ylim = c(0, 7000),
       pch = 0,
       cex = 3,
       cex.axis = 4,
       cex.lab = 4,
       cex.main = 8,
       las = 1)
  
  par(new = TRUE)

  plot(jitter(rep(future_day, length(df2[df2$HarvTime == 6, y])), amount = 1),
       df2[df2$HarvTime == 6, y],
       xlab = "", ylab = "",
       xlim = c(0, 120), ylim = c(0, 7000),
       pch = 4,
       cex = 3,
       cex.axis = 4,
       cex.lab = 4,
       cex.main = 8,
       las = 1)

  par(new = TRUE)

  DAS_seq <- seq(0, max(DF_now$DAS), length.out = 100)
  DAS_seq_fu <- seq(max(DF_now$DAS), 120, length.out = 100)

  fixed_effects <- fixef(fm1now_nlme)
  random_effects <- ranef(fm1now_nlme)

  for(i in 1:nrow(random_effects)) {
    Asym_i <- fixed_effects["Asym"] + random_effects[i, "Asym"]
    b2_i   <- fixed_effects["b2"]   + random_effects[i, "b2"]
    b3_i   <- fixed_effects["b3"]   + random_effects[i, "b3"]

    pred_i    <- SSgompertz(DAS_seq,    Asym_i, b2_i, b3_i)
    pred_i_fu <- SSgompertz(DAS_seq_fu, Asym_i, b2_i, b3_i)

    lines(DAS_seq, pred_i, col = "black", lwd = 1, lty = 1)
    lines(DAS_seq_fu, pred_i_fu, col = "grey", lwd = 1, lty = 2)
  }

  title(xlab = expression("DAS (days)"), line = 8, cex.lab = 5)
  title(ylab = expression(paste("Tuber Fresh Weight ( "*g~m^{-2}*" )")), line = 12, cex.lab = 5)
  
  legend("topleft", 
         legend = c("estimated value", "observed value", "fitted curve", "projected curve"), 
         pch = c(0, 4, NA, NA), 
         lty = c(NA, NA, 1, 2), 
         col = c("black", "black", "black", "grey"), 
         pt.cex = 3, 
         cex = 5,
         bty = "n", 
         lwd = c(3, 3, 3, 3))

  dev.off()
}

```


## _Scatter Plot of Predicted vs. Observed Values
```{r}
make_scatter4 <- function(compe_df, eval_df_now, fitting_name_now){
  
  x_vals <- 1:10000
  
  cor_now <- eval_df_now$r
  r2_now <- eval_df_now$r2
  RMSE_now <- eval_df_now$RMSE
  
  g <- ggplot(compe_df, aes(x=Wei_all_per_m2, y=Prediction))
  g <- g + geom_point() 
  g <- g + geom_abline(slope = 1, intercept = 0) 
  g <- g + xlab(expression(paste("Observed TW ( "*g~m^{-2}*" )"))) +
         ylab(expression(paste("Predicted TW ( "*g~m^{-2}*" )"))) 

  g <- g + scale_x_continuous(limits = c(1000, 8000), breaks = seq(1000, 8000, by = 1000))
  g <- g + scale_y_continuous(limits = c(1000, 8000), breaks = seq(1000, 8000, by = 1000))

  g <- g + theme_bw()
  g <- g + theme(
      aspect.ratio = 1,
      axis.title = element_text(size = 20),       
      axis.text = element_text(size = 16),        
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.ticks.length = unit(-0.2, "cm"),       
      axis.ticks = element_line(color = "black"),  
      panel.grid.major = element_blank(),  
      panel.grid.minor = element_blank()   
  )
  
  g <- g + annotate("text", x = 1600, y = 8000, hjust = 0, vjust = 0.5, size = 6,
                  label = sprintf("'r: %.2f'", cor_now),
                  parse = TRUE)
  g <- g + annotate("text", x = 1600, y = 7300, hjust = 0, vjust = 0.5, size = 6,
                  label = sprintf("R^2: %.2f", r2_now),
                  parse = TRUE)
  g <- g + annotate("text", x = 1600, y = 6600, hjust = 0, vjust = 0.5, size = 6,
                  label = sprintf("RMSE: %.0f", RMSE_now),
                  parse = TRUE)
  
  plot_title <- if (fitting_name_now == "nlsList") {
    "Separate model in 2024"
  } else if (fitting_name_now == "nlme") {
    "Mixed-Effects Model in 2024"
  } else {
    "Model in 2024"
  }
  g <- g + ggtitle(plot_title)
  g <- g + theme(plot.title = element_text(size = 24, hjust = 0.5))
  

  ggsave(
    filename = file.path(results_dir, 
                         paste0("pap_scatter_", fitting_name_now, "_", stra_name_now, ".png")
                         ),
    plot = g,
    width = 1800,
    height = 1600,
    units = "px",   
    dpi = 300       
  )
  
}
```


## _Run plotting figure function in a Loop
```{r}
for (blo_now in c("bloAll")){ 
  if (!(blo_now == "bloAll")) {
    next  
  }
  
  eval_df_all <- data.frame(stra_name = character(0),
                            fitting_name = character(0),
                            r = character(0),
                            r2 = character(0),
                            RMSE = character(0))
  
  
  for (stra_i in 1:length(stra_names_li)){

    
    stra_name_now <- stra_names_li[stra_i]
    if (!(stra_name_now %in% anno_fig_li)) {
    next  
    }
    
    print(stra_name_now)
    
    ml_pred_df <- get_ml_pred_df(modeltime_now_dir,stra_name_now)
    df2 <- df
    df2[cols_Label] <- lapply(df2[cols_Label], as.factor)
    
    if (blo_now != "bloAll"){
      ml_pred_df <- ml_pred_df[ml_pred_df$subblock == str_sub(blo_now, -1),]
      df2 <- df2[df2$subblock == str_sub(blo_now, -1),]
    }
    
    Test_alp <- c("B")
    CV_TorF <- F
    future_day <- 109
    
    DF_now <- make_grouped_byplot(Test_alp = Test_alp, df = ml_pred_df, CV = CV_TorF, future_day = future_day)
    

    make_plot_obs(DF_now, df2, stra_name_now)
    
    # nlsList
    fitting_name_now <- "nlsList"
    fmlnow_lis <- readRDS(file.path(nlslist_obj_dirname,
                                    paste0(fitting_name_now, "_" , stra_name_now, ".rds")
                                    )
                          )
    pred_df_nlsList <- cal_future_y_nlsList(DF_now, fmlnow_lis, future_day)
    make_plot_nlsList4(df2, DF_now, fmlnow_lis, stra_name_now, future_day)
    compe_df_nlsList <- make_compe_df(pred_df_nlsList, df2)
    eval_df_nlsList <- get_eval_values(compe_df_nlsList, stra_name_now, fitting_name_now)
    eval_df_all <- rbind(eval_df_all, eval_df_nlsList)
    make_scatter4(compe_df_nlsList, eval_df_nlsList, fitting_name_now)
    
    # nlme
    fitting_name_now <- "nlme"
    fm1now_nlme <- readRDS(file.path(nlme_obj_dirname,
                                     paste0(fitting_name_now, "_" , stra_name_now, ".rds")
                                     )
                           )
    if (is.null(fm1now_nlme)==FALSE){
      pred_df_nlme <- cal_future_y_nlme(DF_now, fm1now_nlme, future_day)
      make_plot_nlme4(df2, DF_now, fm1now_nlme, stra_name_now, future_day)
      compe_df_nlme <- make_compe_df(pred_df_nlme, df2)
      eval_df_nlme <- get_eval_values(compe_df_nlme, stra_name_now, fitting_name_now)
      eval_df_all <- rbind(eval_df_all, eval_df_nlme)
      make_scatter4(compe_df_nlme, eval_df_nlme, fitting_name_now)
    }
    
    else{
      eval_df_nlme <- get_eval_values(compe_df_nlme, stra_name_now, fitting_name_now, isnull = TRUE)
      eval_df_all <- rbind(eval_df_all, eval_df_nlme)
    }
  }

}
```

## _Create Table of Mean Evaluation Metrics for Tuber Weight Forecasts
```{r}
blo_now <- c("bloAll")
eval_df_all_raw <- read.csv(file.path(results_dir, 
                                      paste0("modeltime_now", "_", modeltime_now, "/",
                                             "eval_df_all", "_", blo_now, ".csv")
                                      )
                            )
eval_df_all_raw
```


```{r}
eval_df_all <- eval_df_all_raw%>%
  mutate(stra_name = str_remove(stra_name, "\\.csv$")) %>% 
  separate(stra_name, into = c("bloCV", "ImgType", "SampRate", "SampMetho", "Rep"),
           sep = "_", remove = FALSE) %>%
  mutate(
    bloCV = sub("bloCV-", "", bloCV),
    ImgType = sub("ImgType-", "", ImgType),
    SampRate = as.integer(sub("SampRate-", "", SampRate)),
    SampMetho = sub("SampMetho-", "", SampMetho),
    Rep = sub("Rep-", "", Rep)
  ) 
print(eval_df_all)
```

Averaging Across Three Replicates
```{r}
summa_eval_df_all <- eval_df_all %>% 
  group_by(bloCV,ImgType, SampRate, SampMetho, fitting_name) %>% 
  summarise(
    mean_r2 = mean(r2, na.rm = TRUE),
    mean_r = mean(r, na.rm = TRUE),
    mean_RMSE = mean(RMSE, na.rm = TRUE),
    sd_r2 = sd(r2, na.rm = TRUE),
    sd_r = sd(r, na.rm = TRUE),
    sd_RMSE = sd(RMSE, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(group = paste(ImgType, SampMetho, fitting_name,sep = "_"))
write.csv(summa_eval_df_all, file.path(results_modeltime_now_dir, 
                                       paste0("summa_eval_df_all.csv")
                                       )
          )
summa_eval_df_all 
```